\section{参考文献}

周纯杰教授相关论文： 

1.[9625843] Zhao, Yue; Zhou, Chunjie; Tian, Yu-Chu; Qin, Yuanqing; Hu, Xiaoya, "$L_2$ Gain Secure Control of Cyber-Physical Systems Under Fast Time-Varying Cyber Attacks," IEEE Transactions on Network Science and Engineering, vo. 9, no. 2, pp. 648-659, 2022.

2.[8270567] Huang, Kaixing; Zhou, Chunjie; Tian, Yu-Chu; Yang, Shuanghua; Qin, Yuanqing, "Assessing the Physical Impact of Cyberattacks on Industrial Cyber-Physical Systems," IEEE Transactions on Industrial Electronics, vo. 65, no. 10, pp. 8153-8162, 2018.

3.[8678699] Huang, Kaixing; Zhou, Chunjie; Qin, Yuanqing; Tu, Weixun, "A Game-Theoretic Approach to Cross-Layer Security Decision-Making in Industrial Cyber-Physical Systems," IEEE Transactions on Industrial Electronics, vo. 67, no. 3, pp. 2371-2379, 2020.


4.[9527096] Zhao, Yue; Du, Xin; Zhou, Chunjie; Tian, Yu-Chu; Hu, Xiaoya; Quevedo, Daniel E., "Adaptive Resilient Control of Cyber-Physical Systems Under Actuator and Sensor Attacks," IEEE Transactions on Industrial Informatics, vo. 18, no. 5, pp. 3203-3212, 2022.

5.[8443136] Li, Xuan; Zhou, Chunjie; Tian, Yu-Chu; Qin, Yuanqing, "A Dynamic Decision-Making Approach for Intrusion Response in Industrial Control Systems," IEEE Transactions on Industrial Informatics, vo. 15, no. 5, pp. 2544-2554, 2019.

6.[7081762] Zhou, Chunjie; Huang, Shuang; Xiong, Naixue; Yang, Shuang-Hua; Li, Huiyun; Qin, Yuanqing; Li, Xuan, "Design and Analysis of Multimodel-Based Anomaly Intrusion Detection Systems in Industrial Process Automation," IEEE Transactions on Systems, Man, and Cybernetics: Systems, vo. 45, no. 10, pp. 1345-1360, 2015.

7.[9266775] Zhou, Chunjie; Hu, Bowen; Shi, Yang; Tian, Yu-Chu; Li, Xuan; Zhao, Yue, "A Unified Architectural Approach for Cyberattack-Resilient Industrial Control Systems," Proceedings of the IEEE, vo. 109, no. 4, pp. 517-541, 2021.

8.[9199295] Hu, Bowen; Zhou, Chunjie; Tian, Yu-Chu; Hu, Xiaoya; Junping, Xinjue, "Decentralized Consensus Decision-Making for Cybersecurity Protection in Multimicrogrid Systems," IEEE Transactions on Systems, Man, and Cybernetics: Systems, vo. 51, no. 4, pp. 2187-2198, 2021.

9.[9865867] Li, Xinge; Hu, Xiaoya; Zhang, Rongqing; Zhou, Chunjie; Yin, Quan; Yang, Liuqing, "A Model-Driven Security Analysis Approach for 5G Communications in Industrial Systems," IEEE Transactions on Wireless Communications, vo. 22, no. 2, pp. 889-902, 2023.

10.[7360925] Zhang, Qi; Zhou, Chunjie; Xiong, Naixue; Qin, Yuanqing; Li, Xuan; Huang, Shuang, "Multimodel-Based Incident Prediction and Risk Assessment in Dynamic Cybersecurity Protection for Industrial Control Systems," IEEE Transactions on Systems, Man, and Cybernetics: Systems, vo. 46, no. 10, pp. 1429-1444, 2016.

11.[1] H. Sun, Y. Huang, L. Han, and C. Zhou, "Few-shot Detection of Anomalies in Industrial Cyber-Physical System via Prototypical Network and Contrastive Learning," arXiv:2302.10601 [cs.CR], Feb. 2023. OnlineOnline. Available: https://arxiv.org/abs/2302.10601.

12.[ZHAO20221245] Yue Zhao, Xin Du, Chunjie Zhou, Yu-Chu Tian, "Anti-saturation resilient control of cyber-physical systems under actuator attacks," Information Sciences, vo. 608, pp. 1245-1260, 2022.

13.[8093698] Zhang, Qi; Zhou, Chunjie; Tian, Yu-Chu; Xiong, Naixue; Qin, Yuanqing; Hu, Bowen, "A Fuzzy Probability Bayesian Network Approach for Dynamic Cybersecurity Risk Assessment in Industrial Control Systems," IEEE Transactions on Industrial Informatics, vo. 14, no. 6, pp. 2497-2506, 2018.

14.[8661651] Zhou, Chunjie; Li, Xuan; Yang, Shuanghua; Tian, Yu-Chu, "Risk-Based Scheduling of Security Tasks in Industrial Control Systems With Consideration of Safety," IEEE Transactions on Industrial Informatics, vo. 16, no. 5, pp. 3112-3123, 2020.

15.[9832509] Zhao, Yue; Zhou, Chunjie; Tian, Yu-Chu; Yang, Jianhui; Hu, Xiaoya, "Cloud-Based Underactuated Resilient Control for Cyber-Physical Systems Under Actuator Attacks," IEEE Transactions on Industrial Informatics, vo. 19, no. 5, pp. 6317-6325, 2023.

16.[9832509] Zhao, Yue; Zhou, Chunjie; Tian, Yu-Chu; Yang, Jianhui; Hu, Xiaoya, "Cloud-Based Underactuated Resilient Control for Cyber-Physical Systems Under Actuator Attacks," IEEE Transactions on Industrial Informatics, vo. 19, no. 5, pp. 6317-6325, 2023.

17.[8700599] Hu, Bowen; Zhou, Chunjie; Tian, Yu-Chu; Qin, Yuanqing; Junping, Xinjue, "A Collaborative Intrusion Detection Approach Using Blockchain for Multimicrogrid Systems," IEEE Transactions on Systems, Man, and Cybernetics: Systems, vo. 49, no. 8, pp. 1720-1730, 2019.

18.[9531435] Zhao, Yue; Zhou, Chunjie; Tian, Yu-Chu; Qin, Yuanqing, "Composite Finite-Time Resilient Control for Cyber-Physical Systems Subject to Actuator Attacks," IEEE Transactions on Cybernetics, vo. 53, no. 2, pp. 1063-1077, 2023.

19.[9760184] Hu, Bowen; Zhou, Chunjie; Tian, Yu-Chu; Du, Xin; Hu, Xiaoya, "Attack Intention Oriented Dynamic Risk Propagation of Cyberattacks on Cyber-Physical Power Systems," IEEE Transactions on Industrial Informatics, vo. 19, no. 3, pp. 2453-2462, 2023.

20.[8998529] Yang, Jun; Zhou, Chunjie; Tian, Yu-Chu; An, Chao, "A Zoning-Based Secure Control Approach Against Actuator Attacks in Industrial Cyber-Physical Systems," IEEE Transactions on Industrial Electronics, vo. 68, no. 3, pp. 2637-2647, 2021.

21.[8106743] Yang, Jun; Zhou, Chunjie; Yang, Shuanghua; Xu, Haizhou; Hu, Bowen, "Anomaly Detection Based on Zone Partition for Security Protection of Industrial Cyber-Physical Systems," IEEE Transactions on Industrial Electronics, vo. 65, no. 5, pp. 4257-4267, 2018.

22.Ma, M., Han, L., \& Zhou, C. (2024). Research and application of artificial intelligence based webshell detection model: A literature review. ArXiv:2405.00066. [Online]. Available:https://api.semanticscholar.org/CorpusID:269484491

23.[DBLP:journals/corr/abs-2404-08224] Mingrui Ma, Lansheng Han, and Chunjie Zhou, "HCL-MTSAD: Hierarchical Contrastive Consistency Learning for Accurate Detection of Industrial Multivariate Time Series Anomalies," CoRR, vo. abs/2404.08224, pp. 1-15, May 2024. DOI: 10.48550/ARXIV.2404.08224. [Online]. Available:https://doi.org/10.48550/arXiv.2404.08224.

24.[Ma2023BTADAB] Mingrui Ma, Lansheng Han, and Chunjie Zhou, "BTAD: A binary transformer deep neural network model for anomaly detection in multivariate time series data," Adv. Eng. Informatics, vol. 56, pp. 101949, 2023. [Online]. Available:https://api.semanticscholar.org/CorpusID:257799004.

25.[Sun2024unsupervisedspatiotemporalstateestimation] H. Sun, Y. Huang, L. Han, C. Fu, and C. Zhou, "Unsupervised Spatio-Temporal State Estimation for Fine-grained Adaptive Anomaly Diagnosis of Industrial Cyber-physical Systems," arXiv:2403.02616 [cs.LG], 2024. [Online]. Available: https://arxiv.org/abs/2403.02616.

【26】Yin, Zhen, Wei Wang, Xiaozhen Lu, and Zhisheng Yin. “Multi-level Collaborative Defense Strategies Against Malicious Traffic in Wireless Edge Networks,” in 2024 IEEE/CIC International Conference on Communications in China (ICCC Workshops), Nanjing, China, January - June, 2024, pp. 185 - 190.

【27】Khodayari, Soheil, Thomas Barber, and Giancarlo Pellegrino. “The Great Request Robbery: An Empirical Study of Client-side Request Hijacking Vulnerabilities on the Web,” in 2024 IEEE Symposium on Security and Privacy (SP), San Francisco, USA, May, 2024, pp. 166 - 184.

【28】Li, Xiulai, Jieren Cheng, Zhaoxin Shi, Jingxin Liu, Bin Zhang, Xinbing Xu, Xiangyan Tang, and Victor S. Sheng. “Blockchain Security Threats and Collaborative Defense: A Literature Review,” in Computers, Materials \& Continua, vol. 76, no. 3, 2023, pp. 2597 - 2629.

【29】Jin, Zizhi, Qinhong Jiang, Xuancun Lu, Chen Yan, Xiaoyu Ji, and Wenyuan Xu. “PhantomLiDAR: Cross-modality Signal Injection Attacks against LiDAR,” in Network and Distributed System Security (NDSS) Symposium 2024, San Diego, CA, USA, February, 2024, pp. 173-198.

【30】Jiang, Feng, Yunsheng Fu, B. B. Gupta, Yongsheng Liang, Seungmin Rho, Fang Lou, Fanzhi Meng, and Zhihong Tian. “Deep Learning Based Multi-Channel Intelligent Attack Detection for Data Security,” in IEEE Transactions on Sustainable Computing, vol. 5, no. 2, April - June 2020, pp. 204 - 211.

【31】A. Ayodeji, Y.-k. Liu, N. Chao, and L.-q. Yang, “A new perspective towards the development of robust data-driven intrusion detection for industrial control systems,” Nuclear Engineering and Technology, vol. 52,no. 12, pp. 2687–2698, 2020.

【32】F. Zhang, H. A. D. E. Kodituwakku, J. W. Hines, and J. Coble, “Multilayer data-driven cyber-attack detection system for industrial control systems based on network, system, and process data,” IEEE Transactions on Industrial Informatics, vol. 15, no. 7, pp. 4362–4369, 2019.

【33】Ayodeji, Y.-k. Liu, N. Chao, and L.-q. Yang. “A new perspective towards the development of robust data-driven intrusion detection for industrial control systems.” Nuclear Engineering and Technology, vol. 52, no. 12, 2020, pp. 2687–2698.

【34】F. Zhang, H. A. D. E. Kodituwakku, J. W. Hines, and J. Coble. “Multilayer data-driven cyber-attack detection system for industrial control systems based on network, system, and process data.” IEEE Transactions on Industrial Informatics, vol. 15, no. 7, 2019, pp. 4362–4369.

【35】D. Chakraborty and H. Elzarka. “Advanced machine learning techniques for building performance simulation: a comparative analysis.” Journal of Building Performance Simulation, vol. 12, no. 2, 2019, pp. 193–207.

【36】A. Sahu, Z. Mao, P. Wlazlo, H. Huang, K. Davis, A. Goulart, and S. Zonouz. “Multi-source multi-domain data fusion for cyberattack detection in power systems.” IEEE Access, vol. 9, 2021.

【37】Yuan, Bin, Maogen Yang, Zhen Xu, Qunjinming Chen, Zhanxiang Song, Zhen Li, Deqing Zou, and Hai Jin. “Leakage of Authorization-Data in IoT Device Sharing: New Attacks and Countermeasure,” in IEEE Transactions on Dependable and Secure Computing, vol. 21, no. 4, , pp. 3196 - 3210，July/August 2024.

【38】Huang, Xianting, Jing Liu, Yingxu Lai, Beifeng Mao, and Hongshuo Lyu. "EEFED: Personalized Federated Learning of Execution\&Evaluation Dual Network for CPS Intrusion Detection," ieee transactions on information forensics and security, vol. 18, 2023, pp. 41-56, 2023.

【39】Mohamed, Ihab, Hesham A. Hefny, and Nagy R. Darwish. "enhancing cybersecurity defenses: a multicriteria decision-making approach to mitre attack mitigation strategy," International Journal of Computer Networks \& Communications (IJCNC), vol.16, no.4, pp.19-35, July 2024.

【40】Shanthalakshmi, M., \& Ponmagal, R. S. "An intelligent dynamic cyber OPEN physical system threat detection system for ensuring secured communication in 6G autonomous vehicle networks," Scientific Reports, vol.14, no.20795, pp.1 - 20, September 2024.

【41】Tyagi, Amit Kumar, \& Sreenath, N. "Cyber Physical Systems: Analyses, challenges and possible solutions," Internet of Things and Cyber-Physical Systems, vol.1, no.1, pp.22 - 33, December 2021.

【42】Guan Xinping, Yang Bo, Chen Cailian, Dai Wenbin, Wang Yiyin, "A comprehensive overview of cyber-physical systems: from perspective of feedback system," IEEE/CAA Journal of Automatica Sinica, vol.3, no.1, pp.1−14, January, 2016.

【43】Xing Wei, Shen Jun, "Security Control of Cyber–Physical Systems under Cyber Attacks: A Survey," Sensors, vol.24, no.12, pp.3815, June, 2024.

【44】Duo Wenli, Zhou MengChu, Abusorrah Abdullah, "A Survey of Cyber Attacks on Cyber Physical Systems: Recent Advances and Challenges," IEEE/CAA Journal of Automatica Sinica, vol.9, no.5, pp.784–800, May, 2022.

【45】马钰锡，张全新，谭毓安，沈蒙. 面向智能攻击的行为预测技术[J]. 软件学报，2020, 31(9): 1-18.

【46】杨挺，刘亚闯，刘宇哲，王成山. 信息物理系统技术现状分析与趋势综述[J]. 电子与信息学报，2021, 43(12): 3393-3406.

【47】刘烃，田决，王稼舟，吴宏宇，孙利民，周亚东，沈超，管晓宏. 信息物理融合系统综合安全威胁与防御研究[J]. 自动化学报，2019, 45(1): 5-24.

【48】蔡星浦，王琦，黄建业，李周. 电力系统网络攻击信息物理双层协同紧急控制方法[J]. 信息与控制，2020, 3(6): 560-569.
